Abstractions for Multi-Sorted Substitutions

### 2024-03-11 paper/paper.tex
Update.

\newenvironment{LibCode*}{%
  \begin{tcolorbox}[%
    colframe=white,%
    boxrule=0.0pt,%
    top=2.5pt,%
    left=2.5pt,%
    bottom=2.5pt,%
    right=2.5pt,%
    boxsep=0pt%
  ]\vspace{-0.2\baselineskip}%
}{%
  \vspace{-1\baselineskip}%
  \end{tcolorbox}%
}

\newenvironment{ExampleCode*}{%
  \begin{tcolorbox}[%
    colframe=white,%
    colback=yellow!5,%
    boxrule=0.0pt,%
    top=2.5pt,%
    left=2.5pt,%
    bottom=2.5pt,%
    right=2.5pt,%
    boxsep=0pt%
  ]\vspace{-0.2\baselineskip}%
}{%
  \vspace{-1\baselineskip}%
  \end{tcolorbox}%
}

@@

  \noindent
  \begin{minipage}{0.5\linewidth}
    \LibCode\KContextLookupI
  \end{minipage}
  \begin{minipage}{0.5\linewidth}
    \LibCode\KContextLookupII
  \end{minipage}
  % \LibCode\KContextLookup

@@

  Given a \ACode{\ACon{TTraversal}}, we can easily instantiate the
  \ACode{\ACon{TKits}} for variables and terms:
  \LibCode\KTypingInstances
  % \LibCode\KTTraversalNotation

@@

  \AppCode\FPreserve
  The interesting parts of the proof are:
  \begin{itemize}
  \item
    There is a strong similarity to the instantiation of
    map traversal \ACode{\AField{\_⋯\_}}. Where \ACode{\AField{\_⋯\_}}
    used \ACode{\AField{`/id}} or \ACode{\AField{\_↑\_}}, we now use their
    preservation lemmas \ACode{\AField{⊢`/id}} or \ACode{\AField{\_∋↑/⊢↑\_}}.
  \item
    The lambda typing constructor \ACode{\ACon{⊢λ}} weakens the type \ACode{t₂} to
    shield it from expression-substitution, requiring us to use the
    \ACode{\AField{⋯-↑-wk}} lemma.
  \item
    The type application constructor \ACode{\ACon{⊢∙}} substitutes \ACode{t₁} into \ACode{t₂},
    requiring us to use \ACode{\AField{dist-↑-⦅⦆}}.
  \end{itemize}
  Finally, we instantiate the \ACode{\ACon{TTraversal}} structure:
  \AppCode\FTTraversal

>>>>

\newenvironment{LibCode*}{%
  \begin{tcolorbox}[%
    colframe=white,%
    boxrule=0.0pt,%
    top=2.5pt,%
    left=2.5pt,%
    bottom=2.5pt,%
    right=2.5pt,%
    before skip=5pt,%
    after skip=5pt,%
    boxsep=0pt%
  ]
}{%
  \end{tcolorbox}%
}

\newenvironment{ExampleCode*}{%
  \begin{tcolorbox}[%
    colframe=white,%
    colback=yellow!5,%
    boxrule=0.0pt,%
    top=2.5pt,%
    left=2.5pt,%
    bottom=2.5pt,%
    right=2.5pt,%
    before skip=5pt,%
    after skip=5pt,%
    boxsep=0pt%
  ]\vspace{-0.2\baselineskip}%
}{%
  \vspace{-1\baselineskip}%
  \end{tcolorbox}%
}

@@

  \noindent
  \begin{minipage}{0.55\linewidth}
    \LibCode\KContextLookupI
  \end{minipage}
  \begin{minipage}{0.45\linewidth}
    \LibCode\KContextLookupII
  \end{minipage}
  % \LibCode\KContextLookup

@@

  Given a \ACode{\ACon{TTraversal}}, we can easily instantiate the
  \ACode{\ACon{TKits}} for variables and terms:
  \LibCode\KTypingInstances

  % \noindent
  % \begin{minipage}[t]{0.5\linewidth}
  % \LibCode\KTypingInstancesI
  % \end{minipage}
  % \begin{minipage}[t]{0.5\linewidth}
  % \LibCode\KTypingInstancesII
  % \end{minipage}

  % \LibCode\KTTraversalNotation

@@

  \AppCode\FPreserve
  The type of \ACode{\ADef{\_⊢⋯\_}} is the same as in the record definition and hence omitted.
  The interesting parts of the proof are:
  \begin{itemize}
  \item
    There is a strong similarity to the instantiation of
    map traversal \ACode{\AField{\_⋯\_}}. Where \ACode{\AField{\_⋯\_}}
    used \ACode{\AField{`/id}} or \ACode{\AField{\_↑\_}}, we now use their
    preservation lemmas \ACode{\AField{⊢`/id}} or \ACode{\AField{\_∋↑/⊢↑\_}}.
  \item
    The lambda typing constructor \ACode{\ACon{⊢λ}} weakens the type \ACode{t₂} to
    shield it from expression-substitution, requiring us to use the
    \ACode{\AField{⋯-↑-wk}} lemma.
  \item
    The type application constructor \ACode{\ACon{⊢∙}} substitutes \ACode{t₁} into \ACode{t₂},
    requiring us to use \ACode{\AField{dist-↑-⦅⦆}}.
  \end{itemize}
  % Finally, we instantiate the \ACode{\ACon{TTraversal}} structure:
  % \AppCode\FTTraversal
